Methods paper for erosion

### 2017-09-22 docs/methods/erosion_methods.tex
worked a bit more on the numerics section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary Integral Equation Formulation} 
\label{sec:bies}
Here we focus on solving the incompressible Stokes equations with
Dirichlet boundary conditions
\begin{alignat*}{3}
  \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
  \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
  \uu &= \ff,  && \xx \in \bd\Omega.
\end{alignat*}
The viscosity $\mu$ sets the time scale, and we will assume that
$\mu=1$.  We start by defining the double-layer potential, which is the
convolution of the stresslet with a function $\eeta:\bd\Omega
\rightarrow \RR^2$,
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
    \label{eqn:velocityDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the unit outward
normal at $\yy$.  For any density function $\eeta$, the double-layer
potential satisfies the incompressible Stokes equations, but the
double-layer potential can not capture velocity fields corresponding to
rigid body motions~\cite{pow-mir1987}.  A standard method to complete
the double-layer potential is to introduce a Stokeslets and rotlets
centered inside each interior body
\begin{align}
  S[\llambda_k,\cc_k] = \frac{1}{4\pi} \left(-\log \rho \II + 
    \frac{\rr \otimes \rr}{\rho^2} \right)\llambda_k
  \quad \text{and} \quad
  R[\xi_k,\cc_k] = \frac{\rr_k^\perp}{\rho^2}\xi_k, 
  \quad k=1,\ldots,M
  \label{eqn:stokeslet_rotlet}
\end{align}
where  $\rr = \xx - \cc_k$, $\cc_k$ is a point inside the $k^{th}$ body,
$\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then, any solution of
the Stokes equations with a Dirichlet boundary condition $\ff$ can be
written as
\begin{align}
  \label{eqn:completed_DLP}
  \uu(\xx) = \DD[\eeta](\xx) + \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
              \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Omega,
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{subequations}
\label{eqn:completed_BIE}
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DD[\eeta](\xx) + 
      \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \bd\Omega, 
      \label{eqn:DLP}\\
  \llambda_k &= \frac{1}{2\pi}\int_{\gamma_k} \eeta(\yy) \, ds_\yy, 
  \label{eqn:stokeslet} \\
  \xi_k &= \frac{1}{2\pi}\int_{\gamma_k} \yy^\perp \cdot \eeta(\yy)
  \, ds_\yy.
  \label{eqn:rotlet}
\end{align}
\end{subequations}
Finally, because of the incompressibility constraint, the boundary
condition must satisfy 
\begin{align*}
  \int_{\bd\Omega} \ff \cdot \nn \, ds_\yy = 0.
\end{align*}
The result is a rank-one null space of~\eqref{eqn:completed_BIE} which
is removed by adding the rank-one modification 
\begin{align}
  \NN_0[\eeta](\xx) = \int_{\Gamma} 
    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy, \quad \xx \in \Gamma.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Computing the Shear Stress, Vorticity, Pressure, and Drag} 
\label{sec:qois}
There are several quantities besides the velocity that need to be
computed.  First, the governing equations~\eqref{eqn:erosionModel}
require the shear stress along $\gamma_k$.  In addition, to study
characteristics of the flow, the vorticity, pressure, and drag must also
be computed.  Once equation~\eqref{eqn:completed_DLP} is solved for the
density function, Stokeslets, and rotlets, all of these quantities can
be computed by evaluating layer potentials that we now derive.

\subsubsection{Shear Stress}
The shear stress is defined by
\begin{align*}
  \tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss,
\end{align*}
where $\ss$ and $\nn$ are the unit tangent and normal vectors,
respectively (Figure~\ref{fig:schematic}).  The velocity field of the
completed double-layer potential~\eqref{eqn:completed_DLP} involves
three terms: the double-layer potential $\DD$, the Stokeslets $S$, and
the rotlets $R$.  We first compute the deformation tensor $\ssigma =
\frac{1}{2}(\nabla\uu + \nabla\uu^T)$ for each of these terms
individually.

@@

\subsubsection{Vorticity}
For the Stokes equations, on boundaries that have a no-slip boundary
condition, the shear stress is equivalent to the vorticity $w = v_x -
u_y$.  Therefore, to compute the $w(\xx)$ for $\xx \in
\overline{\Omega}$, we only need to compute $w(\xx)$ for $\xx\Omega$.
As we did for the shear stress, we compute the vorticity due to the
double-layer potential, Stokeslets, and rotlets individually.  The
vorticity of the double-layer potential~\eqref{eqn:velocityDLP} at
$\xx \in \Omega$ is
\begin{align}
  w^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
    \frac{(\xx \cdot \eeta)(\xx \cdot \nn^\perp) + 
    (\xx \cdot \nn)(\xx \cdot \eeta)}{\rho^4}ds_{\yy}.
  \label{eqn:vorticityDLP}
\end{align}
The vorticity due to the Stokeslet is
\begin{align*}
  w^S(\xx) = -\frac{1}{\pi} \sum_{k=1}^{M} 
    \frac{\rr \cdot \llambda_k^\perp}{\rho^2},
\end{align*}
and the vorticity of a rotlet is zero.  Therefore, once the density
function and Stokeslets are computed, the vorticity at $\xx \in \Omega$
is
\begin{align*}
  w(\xx) = w^\DD(\xx) + w^S(\xx).
\end{align*}

\subsubsection{Pressure}
To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
same procedure used for the shear stress.  We first find the pressure of
the double-layer potential for $\xx \in \Omega$, and the find the jump
that results from taking the limit of $\xx$ to $\xx_0 \in \Gamma$.
Then, we compute the pressure due to the Stokestlet and rotlet
terms~\eqref{eqn:stokeslet_rotlet}.   For $\xx \in \Omega$,
the pressure is
\begin{align}
  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot \eeta(\yy) \,ds_\yy.
  \label{eqn:pressureDLP}
\end{align}
To compute the pressure at $\xx_0 \in \bd\Omega$, we must take the limit
of equation~\eqref{eqn:pressureDLP} when $\xx$ tends to $\xx_0$.  The
limiting value is given by~\cite{qua-bir2014a}
\begin{align*}
  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
\end{align*}
The pressure due to the Stokeslets is
\begin{align*}
  p^S(\xx_0) = \frac{\rr \cdot \llambda}{2\pi\rho^2},
\end{align*}
and the pressure due to the rotlets is zero.  Therefore, once the
density function and Stokeslets are computed, the pressure at a point
$\xx_0 \in \bd\Omega$ is
\begin{align*}
  p(\xx_0) = \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0) + 
              p^{S}(\xx_0).
\end{align*}

\subsubsection{Drag}
\todo[inline]{check all signs in this section.  Fortran code assumes a
normal pointing into the eroding body and a tangent vector that
corresponds to a couterclockwise parameterization}
Finally, with the pressure and shear stress, the drag on a single body
with boundary $\gamma_k$ is
\begin{align*}
  F_D = \int_{\gamma_k} (-p \nn + \tau \ss)\,ds.
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods\label{s:method}} 
There are several 
We discretize the second-kind integral equation~\eqref{eqn:DLP} using a
Nystr\"om method.  The equations for the
Stokeslets~\eqref{eqn:stokeslet} and rotlets~\eqref{eqn:rotlet} are
approximated with the trapezoid rule.  By applying a quadrature method,
this results in a dense linear system which we solve with fast multipole
accelerated GMRES.  Because of the second-kind nature of the integral
equation, the number of GMRES iterations is mesh independent (but not
geometry independent), and the overall complexity of the Stokes solver
is proportional to the cost of a single matrix-vector multiplication.
The shear stress, pressure, and drag must also be computed using
quadrature, and this can be interpreted as a post-processing step once
the density function, Stokeslets, and rotlets are computed.  All the
quadrature methods are described in Section~\ref{sec:quadrature}

@@

\todo[inline]{Describe the upcoming subsections better}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial Discretization}
\todo[inline]{compute all derivatives in spectral space}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature} 
\label{sec:quadrature}
There are several integrals that we need to compute including the
double-layer potential velocity field~\eqref{eqn:velocityDLP}, the shear
stress~\eqref{eqn:shearStressDLP}, vorticity~\eqref{eqn:vorticityDLP},
and the pressure~\eqref{eqn:pressureDLP}.  By using carefully choosing
the quadrature rules, high-order solutions can be computed.  For all the
integrals, the trapezoid rule is used since it achieves spectral
accuracy for smooth periodic functions.  However, care must be taken
when the source point and target points coincide.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary Integral Equation Formulation} 
\label{sec:bies}
Here we focus on solving the incompressible Stokes equations with
Dirichlet boundary conditions
\begin{alignat*}{3}
  \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
  \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
  \uu &= \ff,  && \xx \in \bd\Omega.
\end{alignat*}
The viscosity $\mu$ sets the time scale, and we will assume that
$\mu=1$.  We start by defining the double-layer potential, which is the
convolution of the stresslet with a function $\eeta:\bd\Omega
\rightarrow \RR^2$,
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
    \label{eqn:velocityDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the unit outward
normal at $\yy$.  For any density function $\eeta$, the double-layer
potential satisfies the incompressible Stokes equations, but the
double-layer potential can not capture velocity fields corresponding to
rigid body motions~\cite{pow-mir1987}.  A standard method to complete
the double-layer potential is to introduce a Stokeslets and rotlets
centered inside each interior body
\begin{align}
  S[\llambda_k,\cc_k] = \frac{1}{4\pi} \left(-\log \rho \II + 
    \frac{\rr \otimes \rr}{\rho^2} \right)\llambda_k
  \quad \text{and} \quad
  R[\xi_k,\cc_k] = \frac{\rr_k^\perp}{\rho^2}\xi_k, 
  \quad k=1,\ldots,M
  \label{eqn:stokeslet_rotlet}
\end{align}
where  $\rr = \xx - \cc_k$, $\cc_k$ is a point inside the $k^{th}$ body,
$\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then, any solution of
the Stokes equations with a Dirichlet boundary condition $\ff$ can be
written as
\begin{align}
  \label{eqn:completed_DLP}
  \uu(\xx) = \DD[\eeta](\xx) + \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
              \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Omega,
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{subequations}
\label{eqn:completed_BIE}
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DD[\eeta](\xx) + 
      \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \bd\Omega, 
      \label{eqn:DLP}\\
  \llambda_k &= \frac{1}{2\pi}\int_{\gamma_k} \eeta(\yy) \, ds_\yy,
  \quad k=1,\ldots,M
  \label{eqn:stokeslet} \\
  \xi_k &= \frac{1}{2\pi}\int_{\gamma_k} \yy^\perp \cdot \eeta(\yy)
  \, ds_\yy, \quad k=1,\ldots,M.
  \label{eqn:rotlet}
\end{align}
\end{subequations}
Finally, because of the incompressibility constraint, the boundary
condition must satisfy 
\begin{align*}
  \int_{\bd\Omega} \ff \cdot \nn \, ds_\yy = 0.
\end{align*}
The result is a rank-one null space of~\eqref{eqn:completed_BIE} which
is removed by adding the rank-one modification 
\begin{align}
  \NN_0[\eeta](\xx) = \int_{\Gamma} 
    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy, \quad \xx \in \Gamma.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Computing Quantities of Interest}
\label{sec:qois}
There are several quantities besides the velocity that need to be
computed.  First, the governing equations~\eqref{eqn:erosionModel}
require the shear stress along $\gamma_k$.  In addition, to study
characteristics of the flow, the vorticity, pressure, and drag, and
resistivity will also be computed.  Once
equation~\eqref{eqn:completed_DLP} is solved for the density function,
Stokeslets, and rotlets, all of these quantities can be computed by
evaluating layer potentials that we now derive.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear Stress}
The shear stress is defined by
\begin{align*}
  \tau = -\left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss,
\end{align*}
where $\ss$ and $\nn$ are the unit tangent and normal vectors,
respectively (Figure~\ref{fig:schematic}).  The velocity field of the
completed double-layer potential~\eqref{eqn:completed_DLP} involves
three terms: the double-layer potential $\DD$, the Stokeslets $S$, and
the rotlets $R$.  We first compute the deformation tensor $\ssigma =
\frac{1}{2}(\nabla\uu + \nabla\uu^T)$ for each of these terms
individually.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vorticity}
For the Stokes equations, on boundaries that have a no-slip boundary
condition, the shear stress is equivalent to the vorticity $w = v_x -
u_y$.  Therefore, to compute the $w(\xx)$ for $\xx \in
\overline{\Omega}$, we only need to compute $w(\xx)$ for $\xx\Omega$.
As we did for the shear stress, we compute the vorticity due to the
double-layer potential, Stokeslets, and rotlets individually.  The
vorticity of the double-layer potential~\eqref{eqn:velocityDLP} at
$\xx \in \Omega$ is
\begin{align}
  w^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} 
    \frac{(\xx \cdot \eeta)(\xx \cdot \nn^\perp) + 
    (\xx \cdot \nn)(\xx \cdot \eeta)}{\rho^4}ds_{\yy}.
  \label{eqn:vorticityDLP}
\end{align}
The vorticity due to the Stokeslet is
\begin{align*}
  w^S(\xx) = -\frac{1}{\pi} \sum_{k=1}^{M} 
    \frac{\rr \cdot \llambda_k^\perp}{\rho^2},
\end{align*}
and the vorticity of a rotlet is zero.  Therefore, once the density
function and Stokeslets are computed, the vorticity at $\xx \in \Omega$
is
\begin{align*}
  w(\xx) = w^\DD(\xx) + w^S(\xx).
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Pressure}
To compute the pressure at $\xx \in \overline{\Omega}$, we follow the
same procedure used for the shear stress.  We first find the pressure of
the double-layer potential for $\xx \in \Omega$, and the find the jump
that results from taking the limit of $\xx$ to $\xx_0 \in \Gamma$.
Then, we compute the pressure due to the Stokestlet and rotlet
terms~\eqref{eqn:stokeslet_rotlet}.   For $\xx \in \Omega$,
the pressure is
\begin{align}
  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot \eeta(\yy) \,ds_\yy.
  \label{eqn:pressureDLP}
\end{align}
To compute the pressure at $\xx_0 \in \bd\Omega$, we must take the limit
of equation~\eqref{eqn:pressureDLP} when $\xx$ tends to $\xx_0$.  The
limiting value is given by~\cite{qua-bir2014a}
\begin{align}
  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
  \label{eqn:pressureDLPdiag}
\end{align}
The pressure due to the Stokeslets is
\begin{align*}
  p^S(\xx_0) = \sum_{k=1}^{M}\frac{\rr \cdot \llambda_k}{2\pi\rho^2},
\end{align*}
and the pressure due to the rotlets is zero.  Therefore, once the
density function and Stokeslets are computed, the pressure at a point
$\xx_0 \in \bd\Omega$ is
\begin{align*}
  p(\xx_0) = \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0) + 
              p^{S}(\xx_0).
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Drag}
\todo[inline]{check all signs in this section.  Fortran code assumes a
normal pointing into the eroding body and a tangent vector that
corresponds to a couterclockwise parameterization}
Finally, with the pressure and shear stress, the drag on a single body
with boundary $\gamma_k$ is
\begin{align}
  F_D = \int_{\gamma_k} (-p \nn + \tau \ss)\,ds.
  \label{eqn:drag}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Resistivity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods\label{s:method}} 
There are three main numerical methods that need to developed: the
boundary integral equation solver~\eqref{eqn:completed_BIE}, computing
the quantities of interest in Section~\ref{sec:qois}, and updating the
shape of the eroding bodies with equation~\eqref{eqn:bodyEvolution}.  In
order to compute stable simulations with long time horizons, we use
numerical methods that achieve spectral accuracy in space, second-order
in time, and maintain an equispaced discretization of the bodies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial Discretization}
Each body will be represented with $N_\iin$ points.  Because
the boundary of each body is closed, it can be represented with spectral
accuracy as a Fourier series
\begin{align*}
  \xx^k(\theta) = \sum_{j = -N/2}^{N/2-1} \hat{x}_j^k e^{ij\theta}.
\end{align*}
There are several instances where derivatives of the shape must be
taken, and this is done with spectral accuracy by differentiating the
Fourier series term-by-term
\begin{align*}
  \frac{d\xx^k(\theta)}{d\theta} = 
      \sum_{j = -N/2}^{N/2-1} ij\hat{x}_j^k e^{ij\theta}.
\end{align*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quadrature} 
There are several integrals that need to be evaluated.  This includes
the double-layer potential for target points both
off~\eqref{eqn:velocityDLP} and on~\eqref{eqn:DLP} the $\bd\Omega$, the
shear stress~\eqref{eqn:shearStressDLP}, the
vorticity~\eqref{eqn:vorticityDLP}, the pressure both
off~\eqref{eqn:pressureDLP} and on~\eqref{eqn:pressureDLPdiag} the
boundary, the drag~\eqref{eqn:drag}, and the resistivity.  Most of the
integrands involved in these calculations are both smooth and periodic,
and the suitably adjusted trapezoid rule will result in spectral
accuracy~\cite{tre-wei2014}.

To numerically solve the completed double-layer
potential~\eqref{eqn:completed_BIE}, we start by discretizing each
interior body $\gamma_k$ with $N_\iin$ points, and the outer geometry
$\Gamma$ with $N_\out$ points.  We let $N = MN_\iin + N_\out$ be the
total number of discretization points, and we apply the trapezoid rule
which results in the linear system
\begin{align*}
  \ff(\xx_i^k) = \sum_{\ell = 1}^{M}\sum_{j=1}^{N} 
    K(\xx_i^k,\xx_j^\ell) \eeta(\xx_j^\ell) 
      \Delta s_{j}^{\ell}, \quad i=1,\ldots,N, \: k=1\ldots,M
\end{align*}
where $\Delta s_j^\ell$ is the arclength term of $\gamma_\ell$ at
$\xx_j^\ell \in \gamma_\ell$, or the corresponding term if $\xx_k \in
\Gamma$, and
\begin{align*}
  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2},
\end{align*}
where $\rr = \xx - \yy$, and $\rho = \|\rr\|$, is the kernel of the
double-layer potential.  The Stokeslet~\eqref{eqn:stokeslet} and
rotlet~\eqref{eqn:rotlet} strengths are also discretized with the
trapezoid rule
\begin{align*}
  \llambda_k &= \sum_{k=1}^{N_\iin} \eeta(\xx_k) 
    \Delta s_{k} \quad \text{and} \quad
  \mu_k = \sum_{k=1}^{N_\iin} \xx_k^\perp \cdot
    \eeta(\xx_k) \Delta s_{k}.
\end{align*}
\todo[inline]{need to pick a good notation for the indices}

By applying a quadrature method, this results in a dense linear system
which we solve with fast multipole accelerated GMRES.  Because of the
second-kind nature of the integral equation, the number of GMRES
iterations is mesh independent (but not geometry independent), and the
overall complexity of the Stokes solver is proportional to the cost of a
single matrix-vector multiplication.  The shear stress, pressure, and
drag must also be computed using quadrature, and this can be interpreted
as a post-processing step once the density function, Stokeslets, and
rotlets are computed.  All the quadrature methods are described in
Section~\ref{sec:quadrature}

@@

\label{sec:quadrature}
There are several integrals that we need to compute including the
double-layer potential velocity field~\eqref{eqn:velocityDLP}, the shear
stress~\eqref{eqn:shearStressDLP}, vorticity~\eqref{eqn:vorticityDLP},
and the pressure~\eqref{eqn:pressureDLP}.  By using carefully choosing
the quadrature rules, high-order solutions can be computed.  For all the
integrals, the trapezoid rule is used since it achieves spectral
accuracy for smooth periodic functions.  However, care must be taken
when the source point and target points coincide.
